Numerous variables relating to 2016 election in 2021 US GSS

### 2022-03-18 outputs/paper/paper.Rmd
ggplot

>>>>

```{r}
library(ggplot2)
reduced_data %>%
  ggplot(aes(x = gender, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = degree, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = born_US, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = Family_income, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = nation_education, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = nation_race, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = nation_arms, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = nation_welfare, fill = pres16)) +
  geom_bar()
```
```{r}
reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = pres16)) +
  geom_bar()
```
